### 2025-08-29 sections/3-datasets.tex
minor typos

For Fashion-MNIST, Figure~\ref{fig:results:fashion-mnist-lfd}, we observe that until depth 5, LFD is less than 4. 
It then starts increasing, reaching a peak of about 6 near depth 20.
In comparison, Glove-25 has even lower LFD, as shown in Figure~\ref{fig:results:glove-25-lfd}. 
In particular, Glove-25's LFD is less than 3 for all depths.
Figure~\ref{fig:results:sift-lfd} shows the LFD for Sift, which is higher relative to both Fashion-MNIST and Glove-25, increasing sharply to a peak of 9 around depth 10.
For Random, which has the same cardinality and dimensionality as Sift, LFD starts at 20 the root cluster, and all percentile values decrease linearly with depth until reaching the leaves of the tree.
The spread in LFD starts narrow for the first few depths and widens as depth increases.
Silva, Figure~\ref{fig:results:silva-lfd}, exhibits consistently low LFD;
less than 3 for all depths, hovering near 1 for clusters at depth 40 and deeper.
For the Radio-ML dataset, Figure~\ref{fig:results:radioml-lfd} LFD values show three distinct peaks around an LFD of 12 near depths of 8, 25 and 50.
Each peak is followed by a linear decrease until encountering a sharp spike for the next peak.
Within each of the three spans of depths, the character of Radio-ML is similar to that of Random.

>>>>

For Fashion-MNIST, Figure~\ref{fig:results:fashion-mnist-lfd}, we observe that until depth 5, LFD is less than 4.
It then starts increasing, reaching a peak of about 6 near depth 20.
In comparison, Glove-25 has even lower LFD, as shown in Figure~\ref{fig:results:glove-25-lfd}.
In particular, Glove-25's LFD is less than 3 for all depths.
Figure~\ref{fig:results:sift-lfd} shows the LFD for Sift, which is higher relative to both Fashion-MNIST and Glove-25, increasing sharply to a peak of 9 around depth 10.
For Random, which has the same cardinality and dimensionality as Sift, LFD starts at 20 at the root cluster, and all percentile values decrease linearly with depth until reaching the leaves of the tree.
The spread in LFD starts narrow for the first few depths and widens as depth increases.
Silva, Figure~\ref{fig:results:silva-lfd}, exhibits consistently low LFD;
less than 3 for all depths, hovering near 1 for clusters at depth 40 and deeper.
For the Radio-ML dataset, Figure~\ref{fig:results:radioml-lfd} LFD values show three distinct peaks around an LFD of 12 near depths of 8, 25 and 50.
Each peak is followed by a linear decrease until encountering a sharp spike for the next peak.
Within each of the three spans of depths, the character of Radio-ML is similar to that of Random.

### 2025-08-29 sections/4-results.tex
minor typos

Though the plots in Figure~\ref{fig:results:scaling-plots} present results for each of CAKES's three algorithms separately, the results in the CAKES column in these tables represent the fastest CAKES algorithm at that dataset and cardinality only.

>>>>

Though the plots in Figure~\ref{fig:results:scaling-plots} present results for each of CAKES's three algorithms separately, the results in the CAKES column in these tables represent the fastest CAKES algorithm for that dataset and cardinality only.
